---
title: "scGPS test"
author: "Quan Nguyen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
#A simple workflow of the scGPS
```{r}
#To install from the development version
#devtools::install_github("IMB-Computational-Genomics-Lab/scGPS",auth_token = "yourToken")

devtools::load_all()

#load mixed population 1 (loaded from sample1 dataset, named it as day2)
day2 <- sample1
mixedpop1 <-NewscGPS_SME(ExpressionMatrix = day2$dat2_counts, GeneMetadata = day2$dat2geneInfo,
                     CellMetadata = day2$dat2_clusters)
#load mixed population 2 (loaded from sample2 dataset, named it as day5)
day5 <- sample2
mixedpop2 <-NewscGPS_SME(ExpressionMatrix = day5$dat5_counts, GeneMetadata = day5$dat5geneInfo,
                     CellMetadata = day5$dat5_clusters)
#load gene list (this can be any lists of user selected genes)
genes <-GeneList
genes <-genes$Merged_unique

#select a subpopulation
c_selectID <- 1

#run the test bootstrap
LSOLDA_dat <- bootstrap_scGPS(nboots = 2,mixedpop1 = mixedpop1, mixedpop2 = mixedpop2, genes=genes, c_selectID, listData =list())

#display some results 
names(LSOLDA_dat)
LSOLDA_dat$LassoPredict
LSOLDA_dat$LDAPredict

#summary results LDA
summary_prediction_lda(LSOLDA_dat=LSOLDA_dat, nPredSubpop = 4)

#summary results Lasso
summary_prediction_lasso(LSOLDA_dat=LSOLDA_dat, nPredSubpop = 4)

#summary deviance 
summary_deviance(LSOLDA_dat)


```

# Some references for Vignette documentation (temporarily kept only)

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
